Template for GTEx example on cluster

### 2017-10-05 analysis/GTEXzscoreTemplate.Rmd
Files commited by wflow_commit.

[plot1](flashr2GTEx1.pdf)

[plot2](flashr2GTEx2.pdf)

>>>>

<img src="figure/flashr2GTEx1.pdf" alt="the plot is in analysis/flashr2GTEx1.pdf"  width="4200" height="4200">

<img src="figure/flashr2GTEx2.pdf" alt="the plot is in analysis/flashr2GTEx1.pdf"  width="4200" height="4200">

## an example to run SFA on RCC or PPS

1. go to the folder where the data is.

### sfa wrapper

this example is on PPS cluster

```{r}
SFA.wrapper = function(X, K){
  N = dim(X)[1]
  P = dim(X)[2]

  if(file.exists("SFAout")){
    unlink("SFAout", recursive= T)
  }
  system("mkdir SFAout")

  write.table(X,file="dscsfa.txt",row.names=F,col.names=F)
  # sfa command line on cluster
  # ~/flash/simulation/methods/sfa/src/sfa -gen ./dscsfamix.txt -g 600 -k 1 -n 200 -iter 100 -rand 999 -o ./SFAout/sfa

  # sqrt(mean(( loadings %*% factor - test$L_true%*%t(test$F_true))^2))/sqrt(mean((test$L_true%*%t(test$F_true))^2))
  system(paste("~/flash/simulation/methods/sfa/src/sfa", "-gen", "./dscsfa.txt", "-g", N, "-k", K,
               "-n", P, "-iter", 100, "-rand", 999, "-o", "./SFAout/sfa", sep=" "))

  if(file.info("./SFAout/sfa_F.out")$size == 1){
    return(list(L = 0, F = 0))
  } else{
    Fhat=read.table("./SFAout/sfa_F.out")
    lambda=read.table("./SFAout/sfa_lambda.out")
    Fhat=as.matrix(Fhat)
    lambda=as.matrix(lambda)
    return(list(L = lambda, F = Fhat))
  }

}
```

this is `sfawrapper.R`

### creat run_sfa.R file

```
load("~/flash/dataanalysis/GTeX/EQTLzscore/gtexEQTL_zscore.rds")
setwd("~/flash/dataanalysis/GTeX/EQTLzscore/")
source("./sfawrapper.R")
source("./SFAmixwrapper.R")
Y = t(zscore)
N = dim(Y)[1]
P = dim(Y)[2]

gsfamix = SFAmix.wrapper(Y,30)
gsfa = SFA.wrapper(Y, 30)
saveRDS(gsfa, file = "~/flash/dataanalysis/GTeX/EQTLzscore/sfaGTExzscore.rds")
saveRDS(gsfamix, file = "~/flash/dataanalysis/GTeX/EQTLzscore/sfamixGTExzscore.rds")

```

and run it

```
R CMD BATCH run_sfa.R
```

SFA provide NaN result when set `K = 30` and `K = 26`. (all the $L_i$ and $F_j$ are NaN).
